Bases de Datos Heterogéneas \\ Tarea 2

### 2009-06-15 bdhetero/tarea2/tarea2.tex
pregunta a de tarea2 de bdhetero

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}

@@

% Pregunta 1
 \item

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage{qtree}

@@

% Pregunta a
 \item

\Tree
[.$\Pi_{\text{PELICULA.NOMBRE}}$
  [.{$\sigma$ \\
   PRODUCE.PRESUPUESTO $ = 1000000$ \\
   PRODUCE.AÑO $ = 2004$ {\bf OR} PRODUCE.AÑO $ = 2005$ \\
   COMPAÑIA.NOMBRE $ = $ ``MGM'' \\
   PELICULA.COD\_PELICULA $ = $ PRODUCE.COD\_PELICULA \\
   PRODUCE.COD\_COMPAÑIA $ = $ COMPAÑIA.COD\_COMPAÑIA \\
   }
    [.$\times$
      [.$\times$ PELICULA PRODUCE ]
      COMPAÑIA
    ]
  ]
]

% Pregunta b
 \item

% Pregunta c
 \item

% Pregunta d
 \item

% Pregunta e
 \item

% Pregunta f
 \item

% Pregunta g
 \item

% Pregunta h
 \item

% Pregunta i
 \item

% Pregunta j
 \item

% Pregunta k
 \item
